---
title: "Meta Analysis"
author: "DevonMaloney"
date: "2024-06-26"
output: word_document
---

###ABoVE Biomass Comparative Analysis 
In this analysis, we compare eight datasets: 
  1) Duncanson et al. 2023
  2) Guindon et al. 2023
  3) Kraatz et al. 2022
  4) Matasci et al. 2018 
  5) Soto-Navarro et al. 2020
  6) Spawn and Gibbs 2020 
  7) Wang et al. 2020
  8) Xu et al. 2021

Outline of methods: 


For each dataset: 
  - Reproject dataset to WGS 84 (EPSG 4326) 
  - Create map of dataset footprint
  - Create map of dataset (cropped to Alaska and Canada)
  - If masked, create NA Mask
  - Apply common NA Mask 
  - Calculate zonal statistics of states/proviences/territories 
  - Calculate zonal statistics of EPA ecoregion level 2
  - Create map of Great Slave Lake study area and calculate sum
  - Create map of Alaska fire disturbance area and calculate sum
  - Create map of British Columbia timber harvest area and calculate sum
  - Extract validation points and plot scatterplot

#Install and call required packages
```{r}

#install.packages(c("ggplot2", "RColorBrewer", "sp", "terra", "sf", "viridis", "ggspatial", "broman", "patchwork", "tidyterra", "raster", "cowplot", "dplyr", "stringr", "spdep"))

lapply(c("ggplot2", "RColorBrewer", "sp", "terra", "sf", "viridis", "ggspatial", "broman", "patchwork", "tidyterra", "raster", "cowplot", "dplyr", "stringr", "spdep"), require, character.only = TRUE)

```

#Set up 

```{r}
setwd("~/OSTEM_Summer24/BiomassDatasets")

x = ext(-180, -50, 40, 120)

GSL_ext = ext(-117.7, -117.1, 61.3, 61.6)
p = as.polygons(GSL_ext)
crs(p) ="+init=EPSG:4326"
writeVector(p, 'GSL_ext.shp', overwrite=TRUE)

Fire_ext1 = ext (-144.4, -142, 66.15, 67.0)
p <- as.polygons(Fire_ext1)
crs(p) ="+init=EPSG:4326"
writeVector(p, 'Fire_ext1.shp', overwrite=TRUE)

Harvest_ext = ext(c(-123.8, -123.4, 54.4, 54.6))
p = as.polygons(Harvest_ext)
crs(p) ="+init=EPSG:4326"
writeVector(p, 'Harvest_ext.shp', overwrite=TRUE)
Harvest_ext= read_sf("Harvest_ext.shp")

AlaskaCanada = st_read("OtherSpatialDatasets/CanadaAlaska_Boundaries.shp")
AlaskaCanada  = st_transform(AlaskaCanada , "epsg:4326")

PSPpoints <- read_sf("Validation_plots/PSPpoints.shp")
NFIpoints <-read_sf("Validation_plots/NFIpoints.shp")

```

#Country Boundaries 

```{r}

countries = read_sf("OtherSpatialDatasets/ne_10m_admin_1_states_provinces/ne_10m_admin_1_states_provinces.shp")
countries = subset(countries, name != "Antarctica")
plot(countries[9])

```

#Create Map of the ABoVE Domain

```{r}

AlaskaCanada_sf = read_sf("OtherSpatialDatasets/CanadaAlaska_Boundaries.shp")
studyarea = read_sf("OtherSpatialDatasets/ABoVE_Study_Domain/ABoVE_Study_Domain.shp")

#Map of study area over Alaska and Canada
ggplot(studyarea) +
  geom_sf(data = AlaskaCanada_sf)+
  geom_sf(data = studyarea, aes(fill = Region))+
  scale_fill_manual(name = "Study Domain",
    values = c("Core Region" = "#93dfb8",
                "Extended Region" = "#9aceeb")) +
  ggtitle("Map of ABoVE Study Domain") +
  labs(
    title = "Study Area Domain",
    subtitle = "NASA Arctic and Borael Vulnerability Experiment",
    caption = "Data: NASA ABoVE | Creation: Devon Maloney") +
  theme_void() +
  annotation_scale() +
  annotation_north_arrow(location = "bl", which_north = "true",
  pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"),
  style = north_arrow_fancy_orienteering) +
  #coord_sf(xlim = c(-102.15, -74.12), ylim = c(7.65, 33.97)) +
  theme(plot.title = element_text(hjust = 0.5),
  plot.subtitle = element_text(hjust = 0.5))

```

##Create Map of EPA Ecoregions Level 2

```{r}

EcoRegions = read_sf("OtherSpatialDatasets/WWF_ecoregions_clipped.shp")

#Map of study area over Alaska and Canada
ggplot(EcoRegions) +
  geom_sf(data = EcoRegions, aes(fill = eco_code))+
  labs(title = "EPA Ecoregions Level 2",
    subtitle = "NASA Arctic and Borael Vulnerability Experiment",
    caption = "Data: NASA ABoVE | Creation: Devon Maloney") +
  theme_void() +
  annotation_scale() +
  annotation_north_arrow(location = "bl", which_north = "true",
  pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"),
  style = north_arrow_fancy_orienteering) +
  theme(plot.title = element_text(hjust = 0.5),
  plot.subtitle = element_text(hjust = 0.5), 
  legend.position='none')

```

#Fire Disturbances 

```{r}
BurnAreas = read_sf("OtherSpatialDatasets/fire_selected.shp")
BurnAreas = st_transform(BurnAreas, crs=4326)
#plot(BurnAreas[1])

BurnAreas = BurnAreas %>% mutate(across('Incid_Name', str_replace, 'ZITZIANA', 'Zitziana (2009)'))
BurnAreas = BurnAreas %>% mutate(across('Incid_Name', str_replace, 'BEAVER LOG LAKES', 'Beaver Log Lakes (2013)'))
BurnAreas = BurnAreas %>% mutate(across('Incid_Name', str_replace, 'MOOSEHEART', 'Mooseheart (2018)'))
BurnAreas = BurnAreas %>% mutate(across('Incid_Name', str_replace, 'LLOYD MOUNTAIN', 'Lloyd Mountain (2019)'))

Fire2009 = subset(BurnAreas, BurnAreas$Ig_Date == "2009-06-17")
Fire2013 = subset(BurnAreas, BurnAreas$Ig_Date == "2013-06-22")
Fire2018 = subset(BurnAreas, BurnAreas$Ig_Date == "2018-06-07")
Fire2019 = subset(BurnAreas, BurnAreas$Ig_Date == "2019-06-23")

#BurnArea_ext = ext(BurnAreas)
#-152.219711906879, -150.737250706955, 63.9174610103174, 64.9170700001804
BurnArea_ext = ext(c(-152.719711906879, -150.237250706955, 63.4174610103174, 65.4170700001804))
BurnArea_ext <- as.polygons(BurnArea_ext)
BurnArea_ext <- sf::st_as_sf(BurnArea_ext)
st_crs(BurnArea_ext) = st_crs(BurnAreas)

Fire2009_ext = ext(Fire2009)
Fire2013_ext = ext(Fire2013)
Fire2018_ext = ext(Fire2018)
Fire2019_ext = ext(Fire2019)

```

#Fire Disturbance plot

```{r}

plot_crayons()
print(brocolors("crayons")["Red"])

#main = 
  ggplot(data = BurnAreas) +
  geom_sf(data = BurnAreas, aes(fill = Incid_Name))+
  #geom_sf_text(data = BurnAreas, bg.color = "white", bg.r = 0.25, aes(label=Incid_Name))+
  #geom_sf_label(data  = BurnAreas,aes(label = Incid_Name), label.size  = NA, alpha = 0.5)+
  labs(title = "Wildfire Disturbances", xlab="", ylab="")+
  theme_light()+
  scale_fill_manual(values = c("Zitziana (2009)" = "#efdecd"  ,
                                "Beaver Log Lakes (2013)" = "#ee204d"   ,
                                "Mooseheart (2018)"="#fff44f", 
                                "Lloyd Mountain (2019)" = "#ff7538"), 
                     name = "Fire name")+
  scale_x_continuous(breaks = c(-151.0, -151.5, -152.0))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

#inset = 
  ggplot(data = AlaskaCanada) + 
  geom_sf(data = AlaskaCanada)+
  geom_sf(data = studyarea, linewidth = 0, aes(fill = Region))+
  scale_fill_manual(name = "Study Domain",
      values = c("Core Region" = "#93dfb8",
      "Extended Region" = "#9aceeb")) +
  geom_sf(data = BurnArea_ext, fill = "transparent", color = "black", linewidth = 0.2)+
  geom_sf(data = BurnAreas, fill = "black")+
  xlim (-179.2, -129)+
  ylim (51.2, 71.4)+
  theme_light()+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(), 
    axis.title.x=element_blank(),
    axis.text.x=element_blank(),
    axis.ticks.x=element_blank(), 
    legend.position="none")

```

#Timber Harvest Disturbance Areas

```{r}
HarvestAreas = read_sf("OtherSpatialDatasets/VectorizedFires.shp")

Harvestsubset = subset(HarvestAreas, HarvestAreas$DN == c(2009,2013,2018,2019))
Harvest2009 = subset(HarvestAreas, HarvestAreas$DN == 2009)
Harvest2013 = subset(HarvestAreas, HarvestAreas$DN == 2013)
Harvest2018 = subset(HarvestAreas, HarvestAreas$DN == 2018)
Harvest2019 = subset(HarvestAreas, HarvestAreas$DN == 2019)

Harvestsubset$DN<- as.character(Harvestsubset$DN)

Harvest2009 = sf_intersection(Harvest2009, Harvest_ext)

plot(Harvest2009[2])
plot(Harvest2013[2])
plot(Harvest2018[2])
plot(Harvest2019[2])

```

#Harvest Areas Disturbance Plots

```{r}

plot_crayons()
print(brocolors("crayons")["Red"])

ggplot(data = Harvestsubset) +
  geom_sf(data = Harvestsubset, aes(fill = DN, color = DN))+
  labs(title = "Harvest Disturbances", xlab="", ylab="")+
  scale_fill_manual(values = c("2009" = "#80daeb"  ,
                                "2013" =  "#926eae" ,
                                "2018"="#1f75fe" , 
                                "2019" = "#1a4876"), 
                     name = "Harvest year")+
   scale_color_manual(values = c("2009" = "#80daeb"  ,
                                "2013" =  "#926eae" ,
                                "2018"="#1f75fe" , 
                                "2019" = "#1a4876"))+
  theme_light()+
  scale_x_continuous(breaks = c(-124.6, -124.2, -123.8, -123.4))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggplot(data = Harvestsubset) +
  geom_sf(data = Harvestsubset, aes(fill = DN, color = DN))+
  labs(title = "Harvest Disturbances", xlab="", ylab="")+
  scale_fill_manual(values = c("2009" = "#80daeb"  ,
                                "2013" =  "#926eae" ,
                                "2018"="#1f75fe" , 
                                "2019" = "#1a4876"), 
                     name = "Harvest year")+
   scale_color_manual(values = c("2009" = "#80daeb"  ,
                                "2013" =  "#926eae" ,
                                "2018"="#1f75fe" , 
                                "2019" = "#1a4876"))+
  xlim (-123.66, -123.3696)+ 
  ylim ( 54.48, 54.61)+
  theme_light()+
  #scale_x_continuous(breaks = c(-124.6, -124.2, -123.8, -123.4))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggplot(data = AlaskaCanada) + 
  geom_sf(data = AlaskaCanada)+
  geom_sf(data = studyarea, linewidth = 0, aes(fill = Region))+
  scale_fill_manual(name = "Study Domain",
      values = c("Core Region" = "#93dfb8",
      "Extended Region" = "#9aceeb")) +
  geom_sf(data = Harvest_ext, fill = "white", color = "black", linewidth = 0.2)+
  geom_sf(data = Harvest2009, fill = "black")+
    geom_sf(data = Harvest2013, fill = "black")+
    geom_sf(data = Harvest2018, fill = "black")+
    geom_sf(data = Harvest2019, fill = "black")+
  xlim (-150, -100)+
  ylim (51.2, 71.4)+
  theme_light()+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(), 
    axis.title.x=element_blank(),
    axis.text.x=element_blank(),
    axis.ticks.x=element_blank(), 
    legend.position="none")

```

#Water Bodies

```{r}

WaterBodies = read_sf("OtherSpatialDatasets/AlaskaCanada_WaterBodies_fixed.shp")
WaterBodies = poly2nb(st_make_valid(WaterBodies))
WaterBodies_GSL = st_crop(WaterBodies, GSL_ext)
WaterBodies_Fire1 = st_crop(WaterBodies, Fire_ext)
WaterBodies_Harvest = st_crop(WaterBodies, Harvest_ext)

```

#Duncanson et al. 2023: Setup 

```{r}

Duncanson2023 = rast("Duncanson2023/boreal_agb_202302061675663506_2760.tif")
Duncanson2023 = Duncanson2023[[1]]
#plot(Duncanson2023)

Duncanson2023  <- terra::project(Duncanson2023, WGS84 <- "+init=EPSG:4326")

#Duncanson2023_crop = crop(Duncanson2023, x)
crs((Duncanson2023))==crs(AlaskaCanada)
#Duncanson2023_mask = mask(Duncanson2023_crop, AlaskaCanada)
#plot(Duncanson20233_mask)

```

#Duncanson et al. 2023: Footprint

```{r}

#setwd("/Volumes/Fieldwork/OSTEM")
#DuncansonFootprint = read_sf("OtherSpatialDatasets/DuncansonFootprint.shp")
DuncansonFootprint = read_sf("C:/Users/dvmalone/Documents/OSTEM_Summer24/BiomassDatasets/OtherSpatialDatasets/DucansonFootprint_dissolve.shp")
DuncansonFootprint = st_transform(DuncansonFootprint, crs = 4326)
AlaskaCanada = st_transform(AlaskaCanada, crs = 4326)
DuncansonFootprint =st_intersection(DuncansonFootprint , AlaskaCanada)
plot(DuncansonFootprint )

ggplot(data = DuncansonFootprint)+
  geom_sf(data=AlaskaCanada, linewidth = 1)+
  geom_sf(data=AlaskaCanada, color = "#e5e5e5",linewidth = 0.5 )+
  geom_sf(data =  DuncansonFootprint, fill = "#feffe0",linewidth = 0 ) +
  geom_sf(data = studyarea, linewidth = 0.5, aes(color = Region),  fill= "transparent")+
  scale_color_manual(name = "Study Domain",
    values = c("Core Region" = "#93dfb8",
                "Extended Region" = "#9aceeb")) +
  labs(title = "Footprint Duncanson et al. 2023 Dataset") +
  theme_light()+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())


```

#Duncanson et al. 2023: Great Slave Lake Study Area

```{r}

Duncanson2023_GSLcrop = crop(Duncanson2023, GSL_ext)

ggplot(data = Duncanson2023_GSL)+
  geom_spatraster(data = Duncanson2023_GSL) +
  labs(title = "Great Slave Lake: Duncanson et al. 2023") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     limits=c(0,150), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```

#Duncanson et al. 2023: Fire Disturbance 

```{r}

Duncanson2023_fire1 = rast("Duncanson2023/boreal_agb_202302061675666285_3551.tif")
Duncanson2023_fire2 = rast("Duncanson2023/boreal_agb_202302061675669847_3456.tif")

Duncanson2023_fire1 = Duncanson2023_fire1 [[1]]
Duncanson2023_fire2 = Duncanson2023_fire2 [[1]]

Duncanson2023_fire1  <- terra::project(Duncanson2023_fire1, WGS84 <- "+init=EPSG:4326")
Duncanson2023_fire2  <- terra::project(Duncanson2023_fire2, WGS84 <- "+init=EPSG:4326")

Duncanson2023_fire1crop  = crop(Duncanson2023_fire1, Fire2019_ext)
Duncanson2023_fire2crop  = crop(Duncanson2023_fire2, Fire2019_ext)

ggplot(data = Duncanson2023_fire1crop)+
  geom_spatraster(data = Duncanson2023_fire1crop) +
  geom_spatraster(data = Duncanson2023_fire2crop) +
  geom_sf(data = Fire2019, color = "yellow", fill= "transparent")+
  labs(title = "2019 Fire Disturbance:  Duncanson et al. 2023",
       subtitle = "Biomass estimation: circa 2020") +
  theme_light()+
  scale_fill_viridis(na.value="transparent", 
                     limits=c(0,150), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
 # scale_y_continuous(breaks = c(64.6, 64.7))+
  scale_x_continuous(breaks = c(-151.6, -151.5, -151.4, -151.3, -151.2))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```

#Guindon et al. 2023: Set up

```{r}
Guindon2023footprint = read_sf("Guindon2023/Guindon2023_FootprintGeom.shp")
Guindon2023 = rast("Guindon2023/Guindon2023_wgs.tif")
plot(Guindon2023)

Guindon2023_crop = crop(Guindon2023, x)

plot(Guindon2023_crop)
crs((Guindon2023_crop))==crs(AlaskaCanada)
#Guindon2023_mask = mask(Guindon2023_crop, AlaskaCanada)
#plot(Guindon2023_mask)

```

#Guindon et al. 2023: Extract Validation points

```{r}

Guindon2023_PSP = extract(Guindon2023_crop, PSPpoints)
Guindon2023_NFI = extract(Guindon2023_crop, NFIpoints)

Guindon_PSP =cbind(PSPpoints,Guindon2023_PSP)
Guindon_NFI =cbind(NFIpoints,Guindon2023_NFI)

Guindon_PSP_2010 = Guindon_PSP[Guindon_PSP$meas_year==2010 & Guindon_PSP$AGB<1000,]
Guindon_NFI_2010 = Guindon_NFI[Guindon_NFI$meas_year==2010 & Guindon_NFI$AGB<1000,]

```

#Guindon et al. 2023: Plot validation points

```{r}

ggplot(Guindon_PSP_2010, aes(x = AGB, y = Guindon2023_wgs))+
  geom_bin2d(bins = 70) +
  #geom_point(size = 2, color = "blue", alpha= 0.4) +
  scale_fill_continuous(type = "viridis") +
  theme_classic() +
  labs(title = "PSP Ground Plot AGB x Guindon et al. 2023 AGB", 
       x = "PSP Ground Plot AGB", 
       y = 'Spawn & Gibbs 2020 AGB') +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_smooth(method = "lm", formula = y ~ x,
              size = 6, linewidth = 2, 
              se=FALSE, color="black") +
  stat_poly_eq() 

ggplot(Guindon_NFI_2010, aes(x = AGB, y = Guindon2023_wgs))+
  geom_point() +
  scale_fill_continuous(type = "viridis") +
  theme_classic() +
  labs(title = "NFI Ground Plot AGB x Guindon et al. 2023 AGB", 
       x = "NFI Ground Plot AGB", 
       y = 'Guindon et al. 2023 AGB') +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_smooth(method = "lm", formula = y ~ x,
              size = 6, linewidth = 2, 
              se=FALSE, color="black") +
  stat_poly_eq() 

```

#Guindon et al. 2023: Great Slave Lake Study Areas

```{r}

Guindon2023_GSL = crop(Guindon2023_crop, GSL_ext)

ggplot(data=Guindon2023_GSL)+
  geom_spatraster(data=Guindon2023_GSL) +
  labs(title = "Great Slave Lake: Guindon et al. 2023") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     limits=c(0,150), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```

#Guindon et al. 2023: Timber Harvest Areas

```{r}

Guindon2023_Harvest = crop(Guindon2023_crop, Harvest_ext)

ggplot(data=Guindon2023_Harvest)+
  geom_spatraster(data=Guindon2023_Harvest) +
  labs(title = "Timber Harvest: Guindon et al. 2023") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     limits=c(0,300), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  #scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  #scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```


#Kraatz et al. 2022: Setup

```{r}

Kraatz2022 = rast("Kraatz2022/Great_Slave_Lake_biomass_2017-2020.tif")
Kraatz2022  <- terra::project(Kraatz2022, WGS84 <- "+init=EPSG:4326")
plot(Kraatz2022, main = "Kraatz 2022 Biomass")

```

#Kraatz et al. 2022: Create NA mask (Creates a binary where NA= 0, all other values = 1)

```{r}

Kraatz2022_na0 = raster(Kraatz2022_crop)
Kraatz2022_na0[!is.na(Kraatz2022_na0)]<-1
Kraatz2022_na0[is.na(Kraatz2022_na0)]<-0
plot(Kraatz2022_na0)

```

#Kraatz et al. 2022: Great Slave Lake Study Area

```{r}
Kraatz2022_GSL = crop(Kraatz2022, GSL_ext)

ggplot(data = Kraatz2022_GSL)+
  geom_spatraster(data = Kraatz2022_GSL) +
  labs(title = "Great Slave Lake: Kraatz et al. 2022") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     #limits=c(0,150), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```

#Kraatz et al. 2022: Extract Validation points 

```{r}

Kraatz2022_PSP = extract(Kraatz2022_crop, PSPpoints)
Kraatz2022_NFI = extract(Kraatz2022_crop, NFIpoints)

Kraatz_PSP =cbind(PSPpoints,Kraatz2022_PSP)
Kraatz_NFI =cbind(NFIpoints,Kraatz2022_NFI)

Kraatz_PSP_2010 = Kraatz_PSP[Kraatz_PSP$meas_year==2018 & Kraatz_PSP$AGB<1000,]
Kraatz_NFI_2010 = Kraatz_NFI[Kraatz_NFI$meas_year==2018 & Kraatz_NFI$AGB<1000,]

```

#Kraatz et al. 2022: Plot validation points
```{r}

ggplot(Kraatz_PSP_2010, aes(x = AGB, y = Great_Slave_Lake_biomass_2017.2020))+
  geom_bin2d(bins = 70) +
  #geom_point(size = 2, color = "blue", alpha= 0.4) +
  scale_fill_continuous(type = "viridis") +
  theme_classic() +
  labs(title = "PSP Ground Plot AGB x Kraatz et al. 2022 AGB", 
       x = "PSP Ground Plot AGB", 
       y = 'Spawn & Gibbs 2020 AGB') +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_smooth(method = "lm", formula = y ~ x,
              size = 6, linewidth = 2, 
              se=FALSE, color="black") +
  stat_poly_eq() 

ggplot(Kraatz_NFI_2010, aes(x = AGB, y = Great_Slave_Lake_biomass_2017.2020))+
  geom_point() +
  scale_fill_continuous(type = "viridis") +
  theme_classic() +
  labs(title = "NFI Ground Plot AGB x Kraatz et al. 2022 AGB", 
       x = "NFI Ground Plot AGB", 
       y = 'Guindon et al. 2023 AGB') +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_smooth(method = "lm", formula = y ~ x,
              size = 6, linewidth = 2, 
              se=FALSE, color="black") +
  stat_poly_eq() 

```

#Matasci et al. 2018: Setup

```{r}
setwd("/Volumes/Fieldwork/OSTEM")
Matasci2018 <-rast("Matasci/matasci_4326.tif")
#Matasci2018   <- terra::project(Matasci2018, WGS84 <- "+init=EPSG:4326")
plot(Matasci2018)

```

#Matasci et al. 2018: Raster plot (maybe too big to run in full)
```{r}
ggplot(data = Matasci2018)+
  geom_spatraster(data = Matasci2018) +
  labs(title = "Matasci et al. 2020") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     limits=c(0,150), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  #scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  #scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```

#Matasci et al. 2018: Raster plot (courser spatial resolution 300x300m)
```{r}

Matasci2018_300 <-rast("Matasci/matasci300.tif")
Matasci2018_300   <- terra::project(Matasci2018_300, WGS84 <- "+init=EPSG:4326")

ggplot(data = Matasci2018_300)+
  geom_spatraster(data = Matasci2018_300) +
  labs(title = "Matasci et al. 2020") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     #limits=c(0,150), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  #scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  #scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```

#Matasci et al. 2018: Footprint

```{r}
setwd("/Volumes/Fieldwork/OSTEM")
MatasciBoundaries = read_sf("Matasci/matasciboundary.shp")
MatasciBoundaries = st_transform(MatasciBoundaries, crs = 4326)
AlaskaCanada = st_transform(AlaskaCanada, crs = 4326)
MatasciBoundaries=st_intersection(MatasciBoundaries, AlaskaCanada)
plot(MatasciBoundaries)

ggplot(data = MatasciBoundaries)+
  geom_sf(data=AlaskaCanada, linewidth = 1)+
  geom_sf(data=AlaskaCanada, color = "#e5e5e5",linewidth = 0.5 )+
  geom_sf(data = MatasciBoundaries, fill = "#feffe0",linewidth = 0 ) +
  geom_sf(data = studyarea, linewidth = 0.5, aes(color = Region),  fill= "transparent")+
  scale_color_manual(name = "Study Domain",
    values = c("Core Region" = "#93dfb8",
                "Extended Region" = "#9aceeb")) +
  labs(title = "Footprint Matasci et al. 2018 Dataset") +
  theme_light()+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())


```

#Matasci et al. 2018: Great Slave Lake Study Area

```{r}

Matasci2018_GSL = crop(Matasci2018, GSL_ext)
plot(Matasci2018_GSL)

ggplot(data = Matasci2018_GSL)+
  geom_spatraster(data = Matasci2018_GSL) +
  labs(title = "Great Slave Lake: Matasci et al. 2020") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     limits=c(0,alas150), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())
```

#Soto-Navarro et al. 2020: Setup

```{r}
SotoNavarro2020 <-rast("Soto-Navarro2020/Soto2020_merge.tif")
SotoNavarro2020_crop = crop(SotoNavarro2020, x)
crs((SotoNavarro2020_crop))==crs(AlaskaCanada)
SotoNavarro2020_mask = mask(SotoNavarro2020_crop, AlaskaCanada)
plot(SotoNavarro2020_mask)

```

#Soto-Navarro et al. 2020: Footprint 
```{r}
ggplot(data = countries)+
  geom_sf(data = countries, color = "grey80", linewidth= 1) +
  geom_sf(data = countries, fill= "#ffffe0", color = "#ffffe0")+
  geom_sf(data = studyarea, fill = "transparent", linewidth = 0.7, aes(color = Region))+
  scale_color_manual(name = "Study Domain",
      values = c("Core Region" = "#93dfb8",
      "Extended Region" = "#9aceeb")) +
  labs(title = "Footprint of Soto-Navarro et al. 2020 Dataset") +
  theme_light()+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank())

```

#Soto-Navarro et al. 2020: Great Slave Lake Study Area

```{r}
 
SotoNavarro2020_GSL = crop(SotoNavarro2020_crop, GSL_ext)

ggplot(data = SotoNavarro2020_GSL)+
  geom_spatraster(data = SotoNavarro2020_GSL) +
  labs(title = "Great Slave Lake: Soto-Navarro et al. 2020") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     limits=c(0,150), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```

#Soto-Navarro et al. 2020: Fire Disturbance 

```{r}
#Fire Study area 
Fire2009_ext = ext(c(-151.6, -150.7, 64.25, 64.65))
SotoNavarro2020_crop_fire = crop(SotoNavarro2020_crop, Fire2009_ext)

ggplot(data = SotoNavarro2020_crop_fire)+
  geom_spatraster(data = SotoNavarro2020_crop_fire) +
  geom_sf(data = Fire2009, color = "yellow", fill= "transparent")+
  labs(title = "2009 Fire Disturbance: Soto-Navarro et al. 2020",
       subtitle = "Biomass estimation: 2010") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     limits=c(0,150), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  #scale_y_continuous(breaks = c(65.8, 66.0, 66.2, 66.4))+
  scale_x_continuous(breaks = c(-151.6, -151.4, -151.2, -151.0, -150.8))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```

#Soto-Navarro et al. 2020: Harvest Area
```{r}

SotoNavarro2020_Harvest = crop(SotoNavarro2020_crop, Harvest_ext)

ggplot(data=SotoNavarro2020_Harvest)+
  geom_spatraster(data=SotoNavarro2020_Harvest) +
  labs(title = "Timber Harvest: Soto-Navarro et al. 2020") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     limits=c(0,300), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  #scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  #scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```

#Soto-Navarro et al. 2020: Create NA mask (Creates a binary where NA= 0, all other values = 1)

```{r}

SotoNavarro2020_na0 = raster(SotoNavarro2020_mask)
SotoNavarro2020_na0[!is.na(SotoNavarro2020_na0)]<-1
SotoNavarro2020_na0[is.na(SotoNavarro2020_na0)]<-0
plot(SotoNavarro2020_na0)

```

#Spawn and Gibbs 2020: Setup 

```{r}
SpawnGibbs2020 = rast("SpawnGibbs2020/aboveground_biomass_carbon_2010.tif")
SpawnGibbs2020_crop = crop(SpawnGibbs2020, x)
crs((SpawnGibbs2020_crop))==crs(AlaskaCanada)
SpawnGibbs2020_mask = mask(SpawnGibbs2020_crop, AlaskaCanada)
plot(SpawnGibbs2020_mask)

```

#Spawn and Gibbs 2020: Footprint 

```{r}
ggplot(data = countries)+
  geom_sf(data = countries, color = "grey80", linewidth= 1) +
  geom_sf(data = countries, fill= "#ffffe0", color = "#ffffe0")+
  geom_sf(data = studyarea, fill = "transparent", linewidth = 0.7, aes(color = Region))+
  scale_color_manual(name = "Study Domain",
      values = c("Core Region" = "#93dfb8",
      "Extended Region" = "#9aceeb")) +
  labs(title = "Footprint of Spawn & Gibbs 2020 Dataset") +
  theme_light()+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank())

```

#Spawn and Gibbs 2020: Great Slave Lake Study Area

```{r}

SpawnGibbs2020_GSL = crop(SpawnGibbs2020_crop, GSL_ext)

ggplot(data=SpawnGibbs2020_GSL)+
  geom_spatraster(data=SpawnGibbs2020_GSL) +
  labs(title = "Great Slave Lake: Spawn and Gibbs 2020") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     #limits=c(0,150), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

#Fire Study area 
Fire2009_ext = ext(c(-151.6, -150.7, 64.25, 64.65))
SpawnGibbs2020_crop_fire = crop(SpawnGibbs2020_crop, Fire2009_ext)

ggplot(data = SpawnGibbs2020_crop_fire) +
  geom_spatraster(data = SpawnGibbs2020_crop_fire) +
  geom_sf(data = Fire2009, color = "yellow", fill= "transparent") +
  labs(title = "2009 Fire Disturbance: Spawn & Gibbs 2020",
       subtitle = "Biomass estimation: 2010") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
  #                   limits=c(0,300), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  #scale_y_continuous(breaks = c(65.8, 66.0, 66.2, 66.4)) +
 scale_x_continuous(breaks = c(-151.6, -151.4, -151.2, -151.0, -150.8))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```

#Spawn and Gibbs 2020: Timber Harvest Area
```{r}

SpawnGibbs2020_Harvest = crop(SpawnGibbs2020_crop, Harvest_ext)

ggplot(data=SpawnGibbs2020_Harvest)+
  geom_spatraster(data=SpawnGibbs2020_Harvest) +
  labs(title = "Timber Harvest: Spawn & Gibbs et al. 2020") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                    # limits=c(0,800), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  #scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  #scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```

#Wang et al. 2020: Setup

```{r}

Wang2020 = rast("Wang/Wang2020_31_merge4326.tif")
#Wang2020  <- terra::project(Wang2020, WGS84 <- "+init=EPSG:4326")

crs((Wang2020))==crs(AlaskaCanada)
plot(Wang2020)


```

#Wang et al. 2020: Footprint
```{r}
#WangBoundaries = read_sf("Wangboundingbox.shp")
#WangBoundaries = transform(WangBoundaries, crs = 4326)

ggplot(data = WangBoundaries)+
  geom_sf(data=AlaskaCanada, linewidth = 1)+
  geom_sf(data=AlaskaCanada, color = "#e5e5e5",linewidth = 0.5 )+
  geom_sf(data = WangBoundaries, fill = "#feffe0",linewidth = 0 ) +
  geom_sf(data = studyarea, linewidth = 0.5, aes(color = Region),  fill= "transparent")+
  scale_color_manual(name = "Study Domain",
    values = c("Core Region" = "#93dfb8",
                "Extended Region" = "#9aceeb")) +
  labs(title = "Footprint Wang et al. 2020 Dataset") +
  theme_light()+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

#plot(WangBoundaries)

```

# Wang et al. 2020: Raster plot

```{r}
ggplot(data = Wang2020)+
  geom_spatraster(data = Wang2020) +
  labs(title = "Wang et al. 2020") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     #limits=c(0,150), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  #scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  #scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())
```

#Wang et al. 2020: Great Slave Lake 

```{r}
Wang2020_Bh12v11 = rast("Wang2020/ABoVE_AGB_Bh12v11.tif")
Wang2020_Bh12v11_1 = Wang2020[[1]]
Wang2020_Bh12v11_1  <- terra::project(Wang2020_Bh12v11_1, WGS84 <- "+init=EPSG:4326")
#plot(Wang2020_Bh12v11_1, main = "Wang 2020 Biomass, Tile Bh12v11 [1]")
Wang2020_GSL = crop(Wang2020_Bh12v11_, GSL_ext)

ggplot(data=Wang2020_GSL)+
  geom_spatraster(data=Wang2020_GSL) +
  labs(title = "Great Slave Lake: Wang et al. 2020") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     #limits=c(0,150), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```


#Wang et al. 2020: Fire study area
```{r}
Fire2013_ext = ext(c(-152.319711906879, -151.683235983754, 63.88, 64.12 ))
Wang2020_fire = crop(Wang2020, Fire2013_ext)

ggplot(data=Wang2020_fire)+
  geom_spatraster(data=Wang2020_fire) +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     limits=c(0,15000), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  scale_y_continuous(breaks = c(63.9, 64.0, 64.1))+
  scale_x_continuous(breaks = c(-151.8, -152.0, -152.2, -117.1))+
  geom_sf(data = Fire2013, color = "yellow", fill= "transparent")+
  labs(title = "2013 Fire Disturbance:  Wang et al. 2020",
       subtitle = "Biomass estimation: 2014") +
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```


#Xu et al. 2021: Setup

```{r}
Xu2021 = stack("Xu2021/test10a_cd_ab_pred_corr_2000_2019_v2.tif")
Xu2021_20=Xu2021[[20]]
crs((Xu2021_20))
Xu2021_20 = rast(Xu2021_20)

Xu2021_20  <- terra::project(Xu2021_20, WGS84 <- "+init=EPSG:4326")


Xu2021_crop = crop(Xu2021_20, x)

#plot(Xu2021_crop)
crs((Xu2021_crop))==crs(AlaskaCanada)
Xu2021_mask = mask(Xu2021_crop, AlaskaCanada)
plot(Xu2021_mask)+title("Xu et al. 2021 (cropped)")


```

#Xu et al. 2021: Footprint 

```{r}
ggplot(data = countries)+
  geom_sf(data = countries, color = "grey80", linewidth= 1) +
  geom_sf(data = countries, fill= "#ffffe0", color = "#ffffe0")+
  geom_sf(data = studyarea, fill = "transparent", linewidth = 0.7, aes(color = Region))+
  scale_color_manual(name = "Study Domain",
      values = c("Core Region" = "#93dfb8",
      "Extended Region" = "#9aceeb")) +
  labs(title = "Footprint of Xu et al. 2021 Dataset") +
  theme_light()+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank())

```

#Xu et al. 2021: Great Slave Lake Study Area

```{r}

Xu2021_GSL = crop(Xu2021_crop, GSL_ext)

#Great Slave lake study are 
ggplot(data = Xu2021_GSL)+
  geom_spatraster(data = Xu2021_GSL) +
  labs(title = "Great Slave Lake: Xu et al. 2021") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     limits=c(0,150), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())
```

#Xu et al. 2021: Fire Disturbance 

```{r}

Fire2018_ext = ext(c(-151.3, -150.6, 64.7, 65.0))
Xu2021_fire = crop(Xu2021_crop, Fire2018_ext)

ggplot(data = Xu2021_fire)+
  geom_spatraster(data = Xu2021_fire) +
  geom_sf(data = Fire2018, color = "yellow", fill= "transparent")+
  labs(title = "2018 Fire Disturbance: Xu et al. 2021",
       subtitle = "Biomass estimation: 2019") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                     limits=c(0,150), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  # scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  scale_x_continuous(breaks = c(-151.3, -151.1, -150.9, -150.7))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```

#Xu et al. 2021: Timber Harvest Area

```{r}

Xu2021_Harvest = crop(Xu2021_crop, Harvest_ext)

ggplot(data=SpawnGibbs2020_Harvest)+
  geom_spatraster(data=Xu2021_Harvest) +
  labs(title = "Timber Harvest: Xu et al. 2021") +
  theme_light()+
  scale_fill_viridis(na.value="white", 
                    # limits=c(0,800), 
                     name = "Biomass \n(Mg of C \nper ha)\n") +
  #scale_y_continuous(breaks = c(61.3, 61.4, 61.5, 61.6))+
  #scale_x_continuous(breaks = c(-117.7, -117.5, -117.3, -117.1))+
  theme(plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```
